---
title: "Anomaly detection configuration"
output: html_notebook
---
Here are all libraries and dependecies used in Anomaly Detection project.




---
ANN2 is a library used to congure autoencoder. Using ANN2 it is possible to conduct a
training of general classification and regression neural networks using gradient descent. ANN2 contains Special features include a function for training replicator neural networks and a function for training autoencoders. Multiple activation and cost functions (including Huber and pseudo-Huber) are supported, as well as L1 and L2 regularization, momentum, early stopping and the possibility to specify a learning rate schedule. The package contains a vectorized gradient descent implementation which facilitates faster training through batch learning.
```{r}
#NN and autoencoder library
install.packages("ANN2")

library(ANN2)

#config file with data used in autoencoder configuration
source("3layers_config.R")

```
---


Google cloud configuration. Setting up connection with google cloud, registering to project 'anomaly-detection' and installing library.
TODO: dodaj reszte konfiguracji i notebook z deployem.

```{r}
if (!"cloudml" %in% installed.packages()){
  install.packages("cloudml")
  gcloud_install()
}
library(cloudml)
```


Libraries and tools used to create model with Keras that is based on Tensorflow library.
```{r}
devtools::install_github("rstudio/reticulate", force = TRUE)

#prepare data

library('keras')
library('tensorflow')

```

Following libraries were used for more robust plotting and data analysis.

```{r}
library(dplyr)
library(ggplot2)
library(purrr)
library(caTools)
```