---
title: "3 layers autoencoder model - Keras library"
output: html_notebook
---
```{r}
#clear environment
rm(list=ls())
gc()
```



```{r}
#general
batchSize <- 256
learningRate <-  1e-06
maxEpochs <- 100
lossFunction <- "mean_squared_error"


#The first hidden layer config
firstLayerActivation = "tanh"
firstLayerUnits <- 30

#The first hidden layer config
secondLayerActivation = firstLayerActivation
SecondLayerUnits <- 15

#The first hidden layer config
thirdLayerActivation = firstLayerActivation
ThirdLayerUnits <- firstLayerUnits

FLAGS_THREE <-flags(
  flag_integer("first_units", 30),
  flag_integer("second_units", 15),
  flag_integer("third_units", 30)
)
```

```{r}
#transform data to matrixes

x_train_matrix <- x_train %>% as.matrix()

x_test_matrix <- x_test %>% as.matrix()
```



Model created with Keras library functions. The net contains 3 dense hidden leayers.
```{r}
model <- keras_model_sequential()
model %>%
  layer_dense(units = firstLayerUnits, activation = firstLayerActivation, input_shape = ncol(x_train_matrix)) %>%
  layer_dense(units = SecondLayerUnits, activation = secondLayerActivation) %>%
  layer_dense(units = ThirdLayerUnits, activation = thirdLayerActivation) %>%
  layer_dense(units = ncol(x_train_matrix))

summary(model)

model %>% compile(
  loss = lossFunction,
  optimizer = optimizer_adam(lr = learningRate),
  metrics = 'accuracy'
)

checkpoint <- callback_model_checkpoint(
  filepath = "3layers.hdf5", 
  save_best_only = TRUE, 
  period = 1,
  verbose = 1
)

early_stopping <- callback_early_stopping(patience = 5)
```

```{r}
#fidding model with only normal requests.
model %>% fit(
  x = x_train_matrix,
  y = x_train_matrix, 
  epochs = maxEpochs, 
  batch_size = batchSize,
  validation_split = 0.1
  )
#   validation_data = list(x_test, y_test)
#  callbacks = list(checkpoint, early_stopping)
```

```{r}
array(c(1:10), dim = c(10,1))
```

```{r}
loss <- evaluate(model, x = x_test[y_test == 0,], y = x_test[y_test == 0,])
loss
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
